Capabilities, MMIO and Robust Safety

### 2020-03-24 capability-meetings-notes/10-03/main.tex
meetitng notes: another fix

The wp-rules for \I{Load} and \I{Store} need to be updated consequently. For
instance, the rule for a \I{Load} reading the integer $x$ on a MMIO address $a$
now requires $\tracefrag{t}$ in the pre-condition (for some $t$), and provides
$\tracefrag{(\X{IORead}, a, x) :: t}$ in the post-condition.

>>>>

The wp-rules for \I{Load} and \I{Store} need to be updated consequently. For
instance, the rule for a \I{Load} reading the integer $x$ on a MMIO address $a$
now requires $\tracefrag{t}$ in the pre-condition (for some $t$), and provides
$\tracefrag{t \app (\X{IORead}, a, x)}$ in the post-condition.
